Data Recovery and Pulse Position Modulation with a Photon Number Resolving SNSPD

### 2023-08-22 manuscript.tex
Update on Overleaf.
testing
overleaf update

>>>>

Something unique.

\hypertarget{fig:channel_data}{%
\begin{figure}
\centering
\includegraphics[width=1\textwidth,height=\textheight]{chapter_03/figs_03/8ch_bar_graph_high_power_light.pdf}
\caption[{Fidelity and rates across 8 channel pairs.}]{\textbf{Fidelity and rates across 8 channel pairs} a) Fidelity for the main 8 channel pairs, measured at a high (5.17 Amps) and a low ( 1.2 Amps) SHG pump power setting. Each power setting results in similar \(\mu\) for all channels: \(\mu_{low}\) = 5.6e-5 \(\pm\) 9e-6 and \(\mu_{high}\) = 6.1e-3 \(\pm\) 3e-4. b) Rate metrics for the 8 channel pairs at the same high and low power settings. The range of possible values for distillable entanglement rate is spanned by the yellow regions, bounded above by log-negativity and below by coherent information. Rates shown assume readout of all 4 available interferometer ports, based on data measured using one port each at Alice and Bob}
\label{fig:channel_data}
\end{figure}
}
